---
title: "The Door-to-Door Caravan Sampling Problem"
author: "Alejandro, Dizon, Kuo, Matias, Pena"
date: "May 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction  

Globe is considering to hire a marketing agency to do a door-to-door sampling caravan project to give
out free prepaid SIM cards to households. The objective is to increase the subscriber base of the company while
obtaining a net profit from this project by hoping that the free SIM card samples will eventually be activated in
the future and revenue will flow from the activated SIMs.   
  
### Sampling Strategy  
The marketing agency proposes to do the following sampling system:  
  
* Ten samplers will be deployed per day to a specific barangay. These samplers are paid minimum
wage by the marketing agency. A limit of one barangay per day is to be visited by the team due
to capacity and planning restrictions.
* A work day is 8 hours from 8am to 5pm. From TGT, the ten samplers will be assembled and at
8am will leave BGC to travel to the selected barangay for that day as a Globe Door-to-Door
Caravan. They have to be back by 5pm at TGT. Lunch break is from 12-1pm.  
* When at the Barangay for the day, the ten samplers will start walking around the Barangay
knocking on houses. Assume that the ten samplers go to different households in different streets
within a Barangay within a day.  
* When a sampler calls on a house and it is answered, the standard spiel to be said is: "Good
morning(afternoon) po, andito po ako ngayon para magbigay ng libreng prepaid SIM from
Globe. May libre po siyang PhP 50.00 load for call, text at saka data. Interested po ba sila?" If
the one that answered the door is interested, the sampler hands a free SIM card. Additionally,
the sampler asks for a signature indicating the SIM has been given away. Maximum of one SIM
card per house.  
* The interaction with a house is composed of 3 parts: 1) Waiting to Answer the Door which
usually takes on average 20 seconds, 2) Spiel Talk Time and 3) Signing time which takes around
10 seconds.  
* If not interested or there is no answer after 30 seconds, then the sampler will move to the next
household. Assume that the Sampler walks on average 4 km/hr. Only 10% of the houses don't
answer.  
* If the sampler was able to provide a SIM to the household, that is considered as a hit. Usually
the success rate of the Samplers claimed by the Marketing Agency is 75%. Which means that
7.5 out of 10 households that answered the door, have accepted the free SIM.  
* Only 25% of the SIMs given away are activated after the sampling and on average will provide
a revenue return of PhP 200.00 per year. The 25% value is called conversion rate, and is
estimated by the Marketing Agency.  
* During the entire sampling project, assume that the Caravan has enough SIMs for the day for
all 10 samplers.  
* A SIM card costs PhP 40.00 to manufacture which includes the initial cost of the PhP 50 credit
load.   
* The agency is proposing a PhP 5,000,000 contract with Globe to do the 100 days of sampling
which includes the salaries of the ten samplers, as well as the company's van and a driver.
(Globe's estimates that the agency spends 10,000 per day for the van's utilization which
includes gas, van rental and driver salary). Note further that the PhP 5,000,000 contract does
not include the costs of the SIM cards.

### Algo and code shiz

Blah blah blah 

#### Loading and preprocessing the data  
Additional R packages are required to properly process the data. These packages contain functions that aren't included in the standard R set of packages.

```{r, eval = FALSE, results='hide', message=FALSE, warning=FALSE}
chooseCRANmirror(graphics=FALSE, ind=1)

install.packages("geosphere")
install.packages("dplyr")

```

#### Load the Required Libraries  
It is necessary to load the previously installed R packages. Once called, the functions contained in these packages will now be useful.   

```{r eval = FALSE}
library(dplyr)
library(geosphere)
```

### Set Working Directory

```{r }
setwd("C:/Users/10012191/Desktop/Reproducible class/ReproducibleClassDiscussion")
```

### Download dataset
Download the dataset that will be utilized in this research. Subsequently, read the downloaded dataset in R. 

```{r }
download.file (url = 'https://drive.google.com/file/d/1F23lt9W0cOF7j-iU5nWp1YhuH7bxIcx0/', destfile="h2h.zip")
```

### Extract the dataset  
```{r }
unzip(zipfile = "./h2h.zip")
```


### Load the dataset
```{r }
dataset = read.csv("h2h.csv",skip=1)
```








